---
title: "Homework 1"
author: "Kossi Akplaka"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

```{r load-packages, message=FALSE, warning=FALSE}
library(tidyverse)
library(openintro)
```

 
In this assignment, I'll build the first letters for both my first and last name using point plots in R.  

Since my name is Kossi Akplaka, I'll be building the letters K and A.

## Build letters K and A

Build the letter K
```{r plot letter K}
x=c(rep(0,500),seq(0,1,length.out=500), seq(0,1,length.out=500))
y=c(seq(-1,1,length.out=500),seq(0,1,length.out=500), seq(0,-1,length.out=500))
z=rbind(x,y)
plot(y~x, xlim=c(-3,3), ylim=c(-3,3))
```



Build the letter A

```{r build letter A}
x=c(seq(-1,0,length.out=500),seq(0,1,length.out=500), seq(-.5,.5,length.out=500))
y=c(seq(-1,1,length.out=500), seq(1,-1,length.out=500), rep(0,500))
z=rbind(x,y)
plot(y~x, xlim=c(-3,3), ylim=c(-3,3))
```


Build both letters K and A together in the same plot

```{r}
x=c(rep(-1,500),seq(-1,0,length.out=500), seq(-1,0,length.out=500),seq(1,2,length.out=500),seq(2,3,length.out=500), seq(1.5,2.5,length.out=500))

y=c(seq(-1,1,length.out=500),seq(0,1,length.out=500), seq(0,-1,length.out=500),seq(-1,1,length.out=500), seq(1,-1,length.out=500), rep(0,500))

z=rbind(x,y)
plot(y~x, xlim=c(-3,3), ylim=c(-3,3))


```



Then, write R code that will left multiply (%*%) a square matrix (x) against each of the vectors of points (y). Initially, that square matrix will be the Identity matrix.  
Use a loop that changes the transformation matrix incrementally to demonstrate 1) shear, 2) scaling, 3)  rotation , and 4) projection in animated fashion.  
Hint:  Use x11() to open a new plotting window in R.

```{r}
# Function to plot the vectors
plot_vectors <- function(vectors, title) {
  plot(vectors[2, ], vectors[1, ], xlim = c(-3, 3), ylim = c(-5, 5),   pch = 20)
}

# Extend vectors to homogeneous coordinates
z_homogeneous = rbind(z, rep(1, ncol(z)))

# Identity matrix
identity_matrix = matrix(c(1, 0, 0, 0, 1, 0, 0, 0, 1), nrow = 3, byrow = TRUE)

# Shear, scaling, Rotation, and Projection matrices
shear_matrix = matrix(c(1, 0.5, 0, 0, 1, 0, 0, 0, 1), nrow = 3, byrow = TRUE)
scaling_matrix = matrix(c(1.5, 0, 0, 0, 0.5, 0, 0, 0, 1), nrow = 3, byrow = TRUE)
rotation_matrix = matrix(c(cos(pi/4), -sin(pi/4), 0, sin(pi/4), cos(pi/4), 0, 0, 0, 1), nrow = 3, byrow = TRUE)
projection_matrix = matrix(c(1, 0, 0, 0, 1, 0, 0, 0, 0), nrow = 3, byrow = TRUE)

# Combine all transformation matrices
transformation_matrices = list(identity_matrix, shear_matrix, scaling_matrix, rotation_matrix, projection_matrix)
titles = c("Identity Matrix", "Shear Matrix", "Scaling Matrix", "Rotation Matrix", "Projection Matrix")

# Open a new plotting window
x11()

# Loop through each transformation matrix
for (i in seq_along(transformation_matrices)) {
  transformed_vectors = transformation_matrices[[i]] %*% z_homogeneous
  plot_vectors(transformed_vectors, titles[i])
  Sys.sleep(3)
}

```


